Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-14 paper/main.tex
changes to discussion of anterior vs posterior 2

% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same; it is rephrased now though}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{sounds meh but don't know how do write it better; results of
    correlations are given here already; maybe the short discussion (cf. very
    beginning of discussion) of these correlation could be put here too which
    will saves space in the main text; but mixing methods/results/discussion is
not absolutely "clean"}

@@

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap [and to the anterior
part of significant clusters of the AV contrasts].
% PPA might have submodules
Previous studies provide evidence that the PPA can be devided into functionally
subregions that might process different stimulus features [during visual scene
perception].
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital
visual cortex than the aPPA \citep{baldassano2013differential,
baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.

\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
    anterior-poster axis depending on the publication; in Aminoff (2007, 2013):
    anterior PPA = spatial associations, region anterior to (!) PPA =
    non-spatial associations; in Aminoff (2015): posterior PPA = spatial
associations, anterior PPA = non-spatial associations; hence: complete bullshit;
ignore Aminoff (2015) due to various reasons}

\paragraph{conclusion: subregions}

The PPA is not a functionally homogeneous area but consists of subregions that
``activate selectively to scenes'' and ``cooperate to build a complete
representation of a scene'' \citep{baldassano2013differential}.
%
Their distinct connectivity properties do suggest that each may be involved in
specific aspects of visual and cognitive processing involved in the overarching
goal of scene understanding \citep{baldassano2013differential}.

%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information \citep{baldassano2013differential}. Previous work has shown that PPA
responds to objects that have spatial associations [Aminoff et al. 2007], are
space-defining [Mullally and Maguire 2011], and are navigationally-relevant
[Janzen and Van Turennout 2004]. These types of responses require spatial memory
and cannot be based purely on visual features like object shape.
\citep{baldassano2013differential}.

%
[If anterior PPA is involved in processing spatial context, then space-defining
    or navigationally-relevant objects could activate anterior PPA more strongly
    than our abstract objects, which were unfamiliar and provided no sense of
    context or orientation.
%
Further experiments will be required to determine whether what type of
object-related information is used in this region
\citep{baldassano2013differential}.]

@@

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrast of both contrasts in the retrosplenial cortex (RSC).
% location functionally defined
As a scene-responsive region, the RSC is functionally defined and not
necessarily identical to the anatomically defined retrosplenial cortex [26]
\citep{epstein2008parahippocampal}.
% function
The RSC is strongly active during scene viewing, scene imagery [25] and mental
imagination of navigation through familiar environments [8]
\citep{epstein2008parahippocampal}.
% location
The RSC is located in the retrosplenial cortex, and posterior cingulate region,
near to the point where the calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.
% anatomy of real RSC
The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
the posterior cingulate (BA 23 and 31) [51–56]
\citep{epstein2008parahippocampal}.

>>>>

% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms?"; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same; it is rephrased now though}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{discussion of the regressors correlation at the very beginning of
discussion could be pasted here; will save space there but will mix methods/
results/ discussion here}

@@

\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
    anterior-poster axis depending on publication;
    in Aminoff (2007, 2013):
    anterior PPA = spatial associations,
    region anterior to (!) PPA = non-spatial associations;
    in Aminoff (2015):
    posterior PPA = spatial associations,
    anterior PPA = non-spatial associations;
    hence: complete bullshit;
    ignore Aminoff (2015) due to various reasons}

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap [and to the anterior
part of significant clusters of the AV contrasts].
% PPA might have submodules
Previous studies provide evidence that the PPA can be devided into functionally
subregions that might process different stimulus features [during visual scene
perception].
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be devided into functionally subregions.
% pPPA
Results of your study suggest that the pPPA is more concerned with visual
aspects of spatial information as exclusively inherent in visual stimuli like
pictures or movies.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) inherent in both visual and
verbal stimuli.

@@

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrasts of both stimuli in the retrosplenial cortex (RSC).
% location functionally defined
As a scene-responsive region, the RSC is functionally defined and not
necessarily identical to the anatomically defined retrosplenial cortex [26]
\citep{epstein2008parahippocampal}.
% function
The RSC is strongly active during scene viewing, scene imagery [25] and mental
imagination of navigation through familiar environments [8]
\citep{epstein2008parahippocampal}.
% location
The RSC is located in the retrosplenial cortex, and posterior cingulate region,
near to the point where the calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.
% anatomy of real RSC
The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
the posterior cingulate (BA 23 and 31) [51–56]
\citep{epstein2008parahippocampal}.
